lab_notebook

### 2018-11-15 lab_notebook.Rmd
combine discover turf, edf, rams, upside.
not fully cleaned up yet

# create dataframe with 
itq <- ITQ_projection %>%
  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")

@@

@@

edf_turf_simple <- select(edf_turf_unite, "country", "start_date", "SciName")

colnames(edf_turf_simple) <- c("Country", "programstart", "SciName")

edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart", "SciName"), type = "full")

>>>>

# create dataframe with 
itq <- ITQ_projection %>%
  select("Country", "Year", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")

@@

#load in DiscoverTURFs data

d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx")

@@

edf_turf_simple <- select(edf_turf, "country", "start_date", "SciName", "turf")
#create new column that says "turf" and TRUE or FALSE

colnames(edf_turf_simple) <- c("Country", "programstart", "SciName", "turf")

#combining edf turf data from upside data
edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart", "SciName", "turf"), type = "full")

#combine edf/upside with discover turfs
all_turf_1 <- join(edf_projection_1, d_turfs, by = c("Country", "SciName", "turf"), type = "full")

#change "blank" NAs to real NAs
all_turf_1[is.na(all_turf_1)] <- "NA"

#rearrange columns
all_turf_2 <- all_turf_1[, c(1,3,5,2,6,7,8,9,4)]

#turning NAs from no ITQ data to FALSE

all_turf_2 %>% replace(is.na(.), FALSE)
